\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-03-11 paper.tex
Comment out broken sentence
Add note about ad insertion; this is technically not wording related.
Remove authority key again; the CID is good enough for this purpose under the proposed scheme.

  \item[-] \textbf{CID:} A content identifier.

  \item[-] \textbf{Authority Key:} A public key (hash) which allows for secure authentication of the data (under some implicit chunking schema).

@@

\begin{itemize}
 \item Advertiser identification
 \item Advertising payload matching constraints of given surface.. Some lives offchaining your own server?
 \item Targeting parameter values matching constraints of given surface
 \item Expiry time
 \item Maximum number of impressions
 \item Price per impression
 \item Funds covering maximum expenditure
\end{itemize}

@@

>>>>

  \item[-] \textbf{CID:} A content identifier which allows for secure authentication of the data under some implicit chunking schema.

@@

\begin{itemize}
 \item Advertiser identification
 \item Advertising payload matching constraints of given surface. % FIXME . Some lives offchaining your own server?
 \item Targeting parameter values matching constraints of given surface
 \item Expiry time
 \item Maximum number of impressions
 \item Price per impression
 \item Funds covering maximum expenditure
\end{itemize}

@@

% TODO: Note: the delivery can be interleaved on the distributor node side
% without need for a good actor client; all that is required is:
% a) for the (encrypted) stream to be chunked with some chunk boundaries
%    aligned with the video frames at which ads are to be inserted,
% b) a distributor-readable file describing such ad insertion points, and
% c) some mechamism by which the distributor can resolve which ad to insert
%    based on the downloader ID.
